\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\input{glyphtounicode}

% --- Public/private toggle ------------------------------------------------
% Hide phone number when building a public copy (e.g. for the website).
% Default: private (phone shown). Override from CLI:
%   pdflatex "\def\public{1}\input{cv.tex}"
\newif\ifpublic
\ifdefined\public\publictrue\else\publicfalse\fi
% --------------------------------------------------------------------------

\pagestyle{fancy}
\fancyhf{} \fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{%
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Miłosz Misiek} \\ \vspace{2pt}
    \small Szczecin, Poland $|$ \href{mailto:contact@miloszmisiek.com}{contact@miloszmisiek.com}\ifpublic\else\ $|$ +48 696 472 220\fi \\
    \href{https://miloszmisiek.com}{miloszmisiek.com} $|$
    \href{https://linkedin.com/in/milosz-misiek}{linkedin.com/in/milosz-misiek} $|$
    \href{https://github.com/miloszmisiek}{github.com/miloszmisiek} $|$
    \href{https://www.researchgate.net/profile/Milosz-Misiek}{ResearchGate}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Software engineer working across the full stack on production systems, with a focus on performance and applied AI. Currently building LLM-powered features using RAG and pgvector for Inbox, a real-time communication product. PhD candidate researching ML-based phishing detection --- published in HICSS 2025 and IEEE Access 2026. Former professional mariner who brings a builder's discipline and a researcher's rigor to engineering problems.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Software Engineer}{May 2023 -- Present}
    {Elastic Email}{Szczecin, PL}
    \resumeItemListStart
      \resumeItem{Core engineer on \textbf{Inbox}, a real-time communication product --- owning features across frontend (React/Next.js), backend (Node.js/Express, GraphQL), and data layers (MongoDB, pgvector). Currently developing AI-powered automated communication using Retrieval-Augmented Generation (RAG) and the OpenAI API.}
      \resumeItem{Built a shared component library adopted across product teams and drove infrastructure improvements after identifying performance bottlenecks.}
      \resumeItem{Led migration of the marketing site from WordPress to Next.js 14 --- Lighthouse SEO 83$\rightarrow$100, Performance 86$\rightarrow$92, Best Practices 77$\rightarrow$100.}
    \resumeItemListEnd

  \resumeSubheading
    {Web Developer}{Mar 2023 -- May 2023}
    {Maritime University in Szczecin}{Szczecin, PL}
    \resumeItemListStart
      \resumeItem{Built and delivered v0.0.1 of an internal procurement system (React, Redux, Express, TypeScript, MySQL), deployed on a Debian server. Led development end-to-end to on-time delivery.}
    \resumeItemListEnd

  \resumeSubheading
    {Deck Officer}{Aug 2015 -- Sep 2021}
    {Chevron Shipping Ltd.}{}
    \vspace{2pt}
    \item[]\small\textit{LNG carriers and oil tankers. Safety-critical operations.}\vspace{-4pt}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {West Pomeranian University of Technology in Szczecin}{Oct 2024 -- Oct 2028}
    {PhD Candidate, Computer Science --- Cybersecurity \& Applied ML}{}
    \resumeItemListStart
      \resumeItem{Research: ML-based phishing detection using XGBoost, NLP, and computer vision in multi-layer detection pipelines.}
    \resumeItemListEnd

  \resumeSubheading
    {West Pomeranian University of Technology in Szczecin}{Oct 2022 -- Jun 2024}
    {MSc in Computer Science --- Grade 5 / GPA 4.0}{}

  \resumeSubheading
    {Maritime University in Szczecin}{Oct 2010 -- May 2015}
    {BSc in Nautical Science}{}

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Publications}
\resumeSubHeadingListStart

  \resumeSubheading
    {XGBoost-Based URL Phishing Detection With Cross-Dataset Validation}{2026}
    {\textit{Miłosz Misiek}, Tomasz Hyla --- IEEE Access}{}
    \resumeItemListStart
      \resumeItem{Cross-dataset validation across 760K+ samples reaching 90.7\% accuracy, with 12.6$\times$ faster training and 3.6$\times$ less memory than comparable neural networks. \href{https://doi.org/10.1109/ACCESS.2026.3672690}{10.1109/ACCESS.2026.3672690}}
    \resumeItemListEnd

  \resumeSubheading
    {Preventing Phishing Attacks with Browser-Based URL Detection}{2025}
    {\textit{Miłosz Misiek}, Tomasz Hyla --- HICSS 2025 Proceedings}{}
    \resumeItemListStart
      \resumeItem{Browser extension for real-time phishing URL detection using XGBoost. \href{https://doi.org/10.24251/HICSS.2025.874}{10.24251/HICSS.2025.874}}
    \resumeItemListEnd

  \resumeSubItem{\textbf{Under review:} multi-layer phishing detection combining NLP and computer vision --- CISIM 2026.}

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Technologies}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} TypeScript, JavaScript, Python, SQL \\
    \textbf{Frontend:} React, Next.js, Astro, Redux, TailwindCSS, GraphQL \\
    \textbf{Backend:} Node.js, Express.js, FastAPI, GraphQL, REST, WebSockets \\
    \textbf{Data \& AI:} MongoDB, pgvector, OpenAI API, RAG, XGBoost, PyTorch, NLP, Computer Vision \\
    \textbf{Tooling:} Docker, Git, Linux, CI/CD
  }}
\end{itemize}

\end{document}
